\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
delete 3 refs, add break

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk~\cite{paolacci2010running}, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

Respondents on Mechanical Turk are only paid if the survey organizer approves their response. A control question, asking the respondent to identify the known action of a robot in a video, served as the first satisficing trap to ensure that respondents were truthfully attempting the survey (see~\cite{krosnick1991response}~\cite{krosnick1996satisficing} for more information on satisficing in survey responses). Survey responses were also manually examined to assess whether respondents were responding honestly. We looked at whether respondent responses were outliers when compared to the rest of the group. We also examined the average time taken by each respondent to complete the survey. Overall, we found that all the respondents had made a honest attempt at filling out the rating and we did not reject any responses.

@@

We also use the Interpolation-based Modified Hausdorff distance~\cite{dubuisson1994modified}~\cite{chen2013dynamic}, which is defined as:

@@

{\bf Dynamic Time Warping:} Dynamic Time Warping (DTW) was previously used in a wide varity of applications ranging from speech recognition, gesture recognition, handwriting matching, and can be applied here to compare two different trajectories~\cite{senin2008dynamic}\cite{chen2013dynamic}. It provides a way to compute a distance despite differences in timing of the trajectories as well. DTW computes a mapping of a subset of the waypoints in $\xi_\text{A}$ to a subset of the waypoints in $\xi_\text{B}$ which constitutes the warping path, or

\begin{equation}
\xi_\text{DTW} = \{ (0, 0), (a_i, b_j), \mathellipsis ,(n_A, n_B) \}
\end{equation} where $n_A = |\tj{A}|$ and $n_B = |\tj{B}|$ which are the number of waypoints in the trajectory. More on the construction of the \tj{DTW} can be read in~\cite{senin2008dynamic}\cite{chen2013dynamic}. The DTW feature is the cost of the warping path.

@@

In all, we utilized three different classification frameworks to predict overall ratings - decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. The features of interest in this tree include the DTW distance computed for the wrist (vs. the tool path) denoted by wrist\_tool\_dtw, the Hausdorf distance computed for the end-effector and the max curvature computed for the elbow. Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the wrist\_tool\_dtw feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. Large values of the wrist\_tool\_dtw feature correspond to extra rotations of the wrist as the tool is moving towards the goal - such trajectories are rated as low quality by the human observers. 
The second classification framework we use is a random forest ensemble of trees. This involves randomly dividing the data into several bootstrap training samples and building a tree on each bootstrap sample. Within each boostrapped sample, at each split a subset of features is randomly selected from the full set of features, but only one predictor is used at each split. This brings additional randomness within each tree. The class is chosen by majority vote across all trees. For every tree constructed from a bootstrapped training sample there is one Out of Bag (OOB) error which can be thought of as a test error for every tree. It is estimated internally, during the run. On test data, the random forest method returns 83\% accuracy.

>>>>

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

Respondents on Mechanical Turk are only paid if the survey organizer approves their response. A control question, asking the respondent to identify the known action of a robot in a video, served as the first satisficing trap to ensure that respondents were truthfully attempting the survey (see~\cite{krosnick1996satisficing} for more information on satisficing in survey responses). Survey responses were also manually examined to assess whether respondents were responding honestly. We looked at whether respondent responses were outliers when compared to the rest of the group. We also examined the average time taken by each respondent to complete the survey. Overall, we found that all the respondents had made a honest attempt at filling out the rating and we did not reject any responses.

@@

We also use the Interpolation-based Modified Hausdorff distance~\cite{dubuisson1994modified}, which is defined as:

@@

{\bf Dynamic Time Warping:} Dynamic Time Warping (DTW) was previously used in a wide varity of applications ranging from speech recognition, gesture recognition, handwriting matching, and can be applied here to compare two different trajectories~\cite{senin2008dynamic}. It provides a way to compute a distance despite differences in timing of the trajectories as well. DTW computes a mapping of a subset of the waypoints in $\xi_\text{A}$ to a subset of the waypoints in $\xi_\text{B}$ which constitutes the warping path, or

\begin{equation}
\xi_\text{DTW} = \{ (0, 0), (a_i, b_j), \mathellipsis ,(n_A, n_B) \}
\end{equation} where $n_A = |\tj{A}|$ and $n_B = |\tj{B}|$ which are the number of waypoints in the trajectory. More on the construction of the \tj{DTW} can be read in~\cite{senin2008dynamic}. The DTW feature is the cost of the warping path.

@@

In all, we utilized three different classification frameworks to predict overall ratings - decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. The features of interest in this tree include the DTW distance computed for the wrist (vs. the tool path) denoted by wrist\_tool\_dtw, the Hausdorf distance computed for the end-effector and the max curvature computed for the elbow.

Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the wrist\_tool\_dtw feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. Large values of the wrist\_tool\_dtw feature correspond to extra rotations of the wrist as the tool is moving towards the goal - such trajectories are rated as low quality by the human observers. 
The second classification framework we use is a random forest ensemble of trees. This involves randomly dividing the data into several bootstrap training samples and building a tree on each bootstrap sample. Within each boostrapped sample, at each split a subset of features is randomly selected from the full set of features, but only one predictor is used at each split. This brings additional randomness within each tree. The class is chosen by majority vote across all trees. For every tree constructed from a bootstrapped training sample there is one Out of Bag (OOB) error which can be thought of as a test error for every tree. It is estimated internally, during the run. On test data, the random forest method returns 83\% accuracy.
